---
title: "ImmGenT - data workshop 1"
output: html_document
date: "2023-02-23"
editor_options: 
  chunk_output_type: console
---

Load libraries and set the working diretory where the dataset_clean.Rds data is.
```{r}
library(Seurat)
library(cowplot)

setwd("~/google_drive/ImmgenT/workshop1/")
```

```{r}
sc <- readRDS('dataset_clean.Rds')
```

Structure of sc (Seurat Object)
* Contains RNA data and ADT data (each a seperate assay)
* Contains UMAP coordinates for both RNA and Protein Data
* Contains following metadata for each cell: sample of origin, RNA cluster #, Protein cluster #, Hashtag identity

Similar to Rosetta, we can generate umaps for each of our metadata on both RNA and Protein level

Example: Plot UMAP RNA + color by sample
```{r}
Idents(sc) <- "sample_name"
DimPlot(sc,reduction = "umap_rna")
```

Example 2: Plot UMAP Protein + color by sample

```{r}
Idents(sc) <- "sample_name"
DimPlot(sc,reduction = "umap_adt")
```


Plot Cd4 RNA
```{r}
DefaultAssay(object = sc) <- "RNA"
FeaturePlot(sc, features = 'Cd4', reduction = "umap_rna")
```

Plot CD4 protein
```{r}
DefaultAssay(object = sc) <- "ADT"
FeaturePlot(sc, features = 'CD4', reduction = "umap_adt")
```


Plot Cd4 RNA x samples
```{r, fig.width = 20, fig.height = 30}
DefaultAssay(object = sc) <- "RNA"
p <- FeaturePlot(sc, features = 'Cd4', reduction = "umap_rna", split.by = "sample_name", combine = F)
plot_grid(plotlist = p, ncol=2, label_size = 14)
```


Plot CD4 protein x samples 
```{r, fig.width = 20, fig.height = 30}
DefaultAssay(object = sc) <- "ADT"
p2 <- FeaturePlot(sc, features = 'CD4', reduction = "umap_adt", split.by = "sample_name", combine = F)
plot_grid(plotlist = p2, ncol=2, label_size = 14)
```








